GPU Virtualization in the Cloud (a mejorar el t\'itulo!!!)

### 2015-10-05 paper.tex
openstack module section

\section{GPGPU Service for OpenStack}
\subsection{Managing remote GPUs with OpenStack}
The main idea of this project is to reach a solution that drive us to an scenario pretty similar the one that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecure.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
Thanks to this modular approach, the Compute Module has not been modified, which led into an easily portability to other Cloud Computing environments.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=.9\linewidth]{images/os2.png}
  \caption{Internal Communication among modules}
  \label{fig:internal}
\end{figure}

>>>>

\section{GPGPU Service for OpenStack}
\subsection{Managing remote GPUs with OpenStack}
The main idea of this project is to reach a solution that drive us to an scenario pretty similar the one that could be seen in Figure~\ref{fig:external}, where a new shared service takes part into the OpenStack Architecure.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
Thanks to this modular approach, the Compute Module has not been modified, which led into an easily portability to other Cloud Computing environments.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/os2.png}
  \caption{Internal Communication among modules}
  \label{fig:internal}
\end{figure}
